Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
sec5
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

The second service implemented on Malacology is ZLog, a high-performance
distributed shared-log that is based on the CORFU protocol~\cite{corfu}. A
shared-log is a general, yet powerful abstraction used to build many
distributed systems. However, existing implementations that rely on consensus
algorithms such as PAXOS funnel I/O through a single point introducing a
bottleneck that restricts throughput. In contrast, the CORFU protocol is able
to achieve high throughput network counter service (called a \emph{sequencer})
that avoids all persistent I/O in the common case.

While a full description of the CORFU system is beyond the scope of this
paper, we'll briefly describe the storage interface, sequencer, and recovery
protocol that form the core components of CORFU that we implement within
Malacology:

{\bf Sequencer.}
High-performance in CORFU is achived using a sequencer service that assigns
client log positions by reading from a volatile, in-memory counter which can
run at a very high throughput and at low-latency. Since the sequencer is
centralized, ensuring seiralizability in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that guarantees correctness.  Failures of the sequencer service in CORFU are
handled by a recovery algorithm that recomputes the new sequencer state using
an application-specific custom storage interface to discover the tail of the
log and invalidate stale client requests using an epoch-based protocol.

{\bf Storage Interface.} The storage interface is a critical component in the
CORFU design. Storage devices must provide a \emph{write}-once, random
\emph{read} interface for reading and writing log entries. The key to
correctness in CORFU lies with the enforcement of up-to-date epoch tags on
client requests; requests tagged with out-of-date epoch values are rejected,
and clients are expected to request a new tail from the sequencer after
refreshing state from an auxillary service. This mechanism forms the basis for
sequencer recovery.

@@

@@

%\begin{figure}[htbp]
%\centering
%\includegraphics{figures/overview-zlog.png}
%\caption{This is ZLog.}
%\end{figure}

\subsection{Interface Installation}

>>>>

The second service implemented on Malacology is ZLog, a high-performance
distributed shared-log that is based on the CORFU
protocol~\cite{balakrishnan_corfu_2012}. A
shared-log is a general, yet powerful abstraction used to build many
distributed systems. However, existing implementations that rely on consensus
algorithms such as PAXOS funnel I/O through a single point introducing a
bottleneck that restricts throughput. In contrast, the CORFU protocol is able
to achieve high throughput using a network counter service, called a 
\emph{sequencer}, that avoids all persistent I/O in the common case.

While a full description of the CORFU system is beyond the scope of this
paper, we'll briefly describe the custom storage device interface, sequencer
service, and recovery protocol that form the core components of CORFU that we
implement within Malacology:

{\bf Sequencer.}
High-performance in CORFU is achived using a sequencer service that assigns
log positions to clients by reading from a volatile, in-memory counter which
can run at a very high throughput and at low-latency. And since the sequencer
is centralized, ensuring seiralizability in the common case is trivial.  The
primary challenge in CORFU is handling the failure of the sequencer in a way
that preserves correctness. Failure of the sequencer service in CORFU is
handled by a recovery algorithm that recomputes the new sequencer state using
an application-specific custom storage interface to discover the tail of the
log, while simulatenously invalidating stale client requests using an
epoch-based protocol.

{\bf Storage Interface.} The storage interface is a critical component in the
CORFU design. Clients independently map log positions onto storage devices,
while storage devices provide an intelligent \emph{write}-once, random
\emph{read} interface for accessing log entries. The key to correctness in
CORFU lies with the enforcement of up-to-date epoch tags on client requests;
requests tagged with out-of-date epoch values are rejected, and clients are
expected to request a new tail from the sequencer after refreshing state from
an auxillary service. This mechanism forms the basis for sequencer recovery.

@@

We implement the sequencer service in Malacology as an application-specific
file type that attaches a 64-bit value to the inode state within the Ceph
metadata service.

@@

\subsubsection{Storage Interface Management}

lua snippet
